This is an example of article title

### 2024-05-24 paper/paper.tex
start writing

Blank localization (also known as workpiece referencing) is an essential task when machining parts.
In this step the geometric relation of the tool of a machine (mill, lathe etc.) and the workpiece(s) needs to be precisely defined/searched. We introduced the concept of multi operation blank localization to address this task for drilling and milling scenarios in a mostly automated way.
The heart of the procedure is a convex quadratically constrained quadratic program (QCQP).
To easily access the solver, the BlankLocalizationCore.jl package was developed.
Its flexibility and extensibility make it an excellent research tool, that can be deployed in production as well.

@@

The \LaTeX{} document preparation system is a special version of the
\TeX; typesetting program where-in a collection of \TeX; commands
are added to \LaTeX{} to simplify typesetting. Importantly, it allows
the author to concentrate on the logical structure of the document
rather than its visual layout.\vskip 6pt
Moreover, \LaTeX{} provides a consistent and comprehensive document
preparation interface. There are simple-to-use commands for
generating a table of contents, lists of figures and/or tables, and indexes.
\LaTeX{} can automatically number list entries, equations, figures,
tables, and footnotes, as well as articles, sections, and subsections.
Using this numbering system, bibliographic citations, page
references, and cross references to any other numbered entity (e.g.
article, section, equation, figure, list entry, etc.) become quite simple
and straightforward. The use of \LaTeX{} document classes allows
a simple change of class to transform the appearance of your document.\vskip 6pt
\LaTeX{} is a powerful tool for managing long and complex documents.
In particular, partial processing enables long documents to
be produced article by article without losing sequential information.
The use of document classes allows a simple change of style
(or style option) to transform the appearance of your document.

\section{The JuliaCon Article Class}
\label{sec:documentclass}
%
The juliacon class file preserves the standard LATEX{} interface such
that any document that can be produced using the standard LATEX{}
article class can also be produced with the class file.\vskip 6pt
It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.\vskip 6pt
Use should be made of symbolic references (\verb|\ref| ) in order to
protect against late changes of order, etc.

\section{USING THE JuliaCon Article CLASS FILE}

>>>>

Blank localization (also known as workpiece referencing) is an essential task in machining.
In this step the geometric relation of the tool of a machine (mill, lathe etc.) and the workpiece(s) needs to be precisely defined/searched.
We introduced the concept of multi operation blank localization to address this task for drilling and milling scenarios in a semi-automated way.
It processes measurement of the rough geometry and the machining CNC code to solve a convex quadratically constrained quadratic program (QCQP).
It gives an optimal solution for given machining allowance - tolerance error, providing a tool for the machinist to find the appropriate balance between the two.
The flexibility and extensibility of the Julia language helped the development of this algorithm, materializing in the \pkg{BlankLocalizationCore} package.
Its flexibility and ease of use make it an excellent research tool, that can be deployed in production as well.

@@

Cast parts can have small geometric variations from lot-to-lot, therefore it is required to alter the machining CNC code to adapt it to each lot.
Current practices include human work (long, possible scrap, needs highly trained workers), and automated methods for parts like wind turbines (measurement of the whole part, mini-max/maxi-min optimizations for large free form surfaces).
The multi operation blank localization method is introduced to focus on drilling and milling scenarios covering a wide range of suitable parts.
To better understand the package, a short description of the multi operation blank localization algorithm is given.
The algorithm needs to balance between machining allowance and tolerance error.
Machining allowance is calculated for each feature as the smallest thickness of the material to be removed.
Tolerance error is defined for each dimensional tolerance record, that is defined between to features.
Their distance has a nominal value and upper-lower bounds.
The goal of the algorithm is to keep the tolerance distances close to the nominal value, while keeping a minimum machining allowance value.

\section{Approach}
\label{sec:approach}
%
The package needs to support the quick prototyping needs of research, while giving a strong/stable baseline/background to validate the concept in the industry as well (high-level, programozói igények nélkül, amit egy menedzser felsorolna):

\begin{itemize}
	\item Model the problem, including geometry representation, qcqp model building and solving, evaluation, visualization.
	\item Modeling the different behavious of the geometries (holes, planes)
	\item Handle two basic types of measurements: primitive or free-form.
	\item Support for importing geometries: all kinds of measurement (expandable/extendable? type system for introducing new measurement types)
\end{itemize}

Tasks are defined in the workpiece coordinate frame (called workpiece datum).
Two types of geometries need to be aligned: rough and machined. Currently the algorithm, thus the implementation supports two types of features: holes and planes. 
A flexible type system is implemented: abstract types are defined and all methods act on them, so implementing a new geometry type (for example to handle point cloud measurement of a rough hole) means defining the type and those methods.
All other functionality of the package are working automatically: setting up the optimization model, solving it, evaluating the results in details and visualizing the geometries.

\section{Results}
The following figures show the same part measured with different techniques, such as laser scanner and coordinate measurement arm.
Based on the package, geometries for both measurement types can be implemented in just a few lines, and the optimization can be run on them.
Two papers have been published using this tool \cite{cserteg:2023_Annals} for primitive types and \cite{cserteg:2023_CMS} for free-form surfaces.

\section{}
